R Notebook

### 2023-10-20 codeTutorial.Rmd
adding code tutorial to readme

---
title: "R Notebook"
output: html_notebook
---

@@

```{r, setup, include=FALSE}
knitr::opts_knit$set(root.dir = '../')
library("viridis") 
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(dplyr)
library(dagitty)
library(tidyverse)
library(magrittr)
library(kableExtra)
library(ggpubr)
library(ggExtra)
library(ggthemes)
library(ggforce)
library(rethinking)
library(latex2exp)
library(Hmisc)
library(grid)

@@

```{r cosineDistributions6d,echo=FALSE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "75%", warning = FALSE, message = FALSE}

@@

Define a function to clean the data.

@@

Define a function to build models.

@@

Build exemplary model and save it.

```{r}
modelGenderGoogle <- buildModel(genderGoogle)
saveRDS(modelGenderGoogle, file = "models/modelGenderGoogle.RDS")
```

>>>>

---
title: "R Notebook"
output:
  md_document:
    variant: markdown_github
---

@@

```{r, setup, echo = TRUE, eval = FALSE}
library("viridis") 
library(ggplot2)
library(ggthemes)
library(gridExtra)
library(dplyr)
library(dagitty)
library(tidyverse)
library(magrittr)
library(kableExtra)
library(ggpubr)
library(ggExtra)
library(ggthemes)
library(ggforce)
library(rethinking)
library(latex2exp)
library(Hmisc)
library(grid)

@@

```{r cosineDistributions6d,echo=TRUE,eval=TRUE,fig.align = "center",cache=TRUE, fig.show = "hold", out.width = "75%", warning = FALSE, message = FALSE, results= 'hide'}

@@

Clean the data.

@@

Define a function to build a model.

@@

Build exemplary model and save it to an otherwise empty `models` folder.

```{r, eval = FALSE, echo = TRUE}
modelGenderGoogle <- buildModel(genderGoogle)
saveRDS(modelGenderGoogle, file = "models/modelGenderGoogle.RDS")
```
